Triptych: logarithmic-sized linkable ring signatures with applications

### 2020-04-07 paper/iacr.tex
Moved files for Arcturus to separate branch

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
Define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
\end{itemize}

@@

Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions as a function of the anonymity set size $N$ and batch size $B$.
Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signaure auxiliary data in such a protocol may differ based on particular implementations.

>>>>

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
Set $$\{a_{j,0}\}_{j=0}^{m-1} \equiv -\sum_{i=1}^{n-1} a_{j,i}$$ and define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
\end{itemize}

@@

Table \ref{table:size} compares proof/signature sizes and verification complexity for these constructions as a function of the anonymity set size $N$ and batch size $B$.
Verification complexity is separated into the number of hash-to-$\F$ operations (denoted $\hs$), hash-to-$\G$ operations (denoted $\hp$), and $i$-multiscalar multiplication operations of size $k(i)$.
Figure \ref{fig:size} examines size as a function of input anonymity set size, under the assumption that elements of both $\G$ and $\F$ occupy $32$ kB of space.
We note that although RingCT 3.0 proofs are slightly smaller for large $N$, Triptych proofs are smaller for $N < 512$, a limited but reasonable range given practical verification times.
We also note that the application of Triptych in a complete transaction protocol is not directly compared to RingCT 3.0 here, as the use of non-proof/signature auxiliary data in such a protocol may differ based on particular implementations.
